### 2021-05-26 about/vita.tex
New paper

\leftright{Citizen of Canada and Singapore}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{Webpage: marcelgoh.github.io}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton-Watson trees. {\sl arXiv preprint 2007.05681}.
Submitted July 2020.
\subitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}.
Submitted December 2020.

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars over the year, discussing
various topics related to branching
processes. (Gave a presentation at five of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, and two on graph regularity.)
[S1]

>>>>

\leftright{Citizen of Canada and Singapore}{3660 Rue Hutchison, Apt.\ 4}
\leftright{Email: marcel\_goh@yahoo.ca}{Montr\'eal, QC H2X 2H3, Canada}
\leftright{Webpage: marcelgoh.ca}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\pubbegin S
\subitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. {\sl arXiv preprint 2007.05681}.
Submitted July 2020.
\subitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set. {\sl arXiv preprint 2012.12339}.
Submitted December 2020.
\subitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}.
Submitted May 2021.

@@

\leftright{\bf Probabilistic analysis of branching processes}{\bf May 2020 -- present}
\leftright{\sl Research group}{\sl McGill University}
\smallskip
Ongoing research on branching processes, headed by Luc Devroye. Studied estimation problems
on Galton-Watson trees. Attended informal seminars over the year, discussing
various topics related to branching
processes. (Gave a presentation at five of these: one on root estimation in Galton-Watson
trees, two on generating functions and elementary analytic combinatorics, and two on graph regularity.)
[S1, S3]
